\section{Work performed}
\label{sec:work_performed}
In previous chapters we have seen the design and development of a web platform for the creation of a system of e-commerce.
\newline
The platform designed, X-commerce, has been realized with the newest technologies in both the client and server side.
\newline
As already mentioned, thanks to the Web components, the complexity of the project has been managed in separate and self-contained. In this way every element hides the operating logic and you can use it by simply inserting a tag on the page. This technique allows you to dial the complexity of the pages to define reusable elements.
\newline
Server-side benefits are represented by the easy way of API creation: describing procedures and model definitions are direct and can generate API and behavioural elements as well.
Finally, the union between server-side and client-side technologies allowed
to create vertical elements that cross all the architectural stack.
At the moment x-commerce, is the core of the e-commerce and implements the basic functions such as:
\begin{itemize}
\item insert, delete, update of new products, vendors, collections, coupons, product type, product options, etc ...
\item possibility to create, delete and manage the list of desires;
\item login with email and password;
\item login passwordless login via SMS and email;
\item possibility to generate variations of a product;
\item implements two payment systems: Braintree and Stripe;
\item implements the possibility to perform tasks in the event of a failure of some operation.
\item etc...
\end{itemize}